### 2016-12-13 poster/poster.tex
Adding numbers to poster (still need to do dynet)

As expected for neural networks, most of the runtime is spent in
matrix multiplication (variants of \texttt{magma\_lds128\_sgemm\_kernel}).

@@

\begin{tabularx}{\textwidth}{l|r}
\textbf{Framework}  & \textbf{Percent time spent in matrix multiply} \\  \hline
TensorFlow  &  ... \\
Theano  & ... \\
DyNet   & ... \\
\end{tabularx}

@@

\begin{tabularx}{\textwidth}{c|ccc}
Metric 										& Dynet & TensorFlow & Theano \\ \hline
\texttt{\detokenize{achieved_occupancy}}			&		.	&		.			&		.		\\
\texttt{\detokenize{sm_efficiency}}					&		.	&		.			&		.		\\
\texttt{\detokenize{warp_efficiency}}					&		.	&		.			&		.		\\
\texttt{\detokenize{warp_nonpred_efficiency}}	&		.	&		.			&		.		\\
\texttt{\detokenize{global_hit_rate}}					&		.	&		.			&		.		\\
\texttt{\detokenize{local_hit_rate}}					&		.	&		.			&		.		\\
\texttt{\detokenize{dram_read_throughput}}		&		.	&		.			&		.		\\
\texttt{\detokenize{dram_write_throughput}}		&		.	&		.			&		.		
\end{tabularx}

>>>>

As expected for neural networks, most of the runtime is spent in
matrix multiplication. Focusing on the most frequent function call
(a variant of \texttt{magma\_lds128\_sgemm\_kernel}):

@@

\begin{tabularx}{\textwidth}{l|r}
\textbf{Framework}  & \textbf{Percent time spent in top \texttt{magma\_lds128...}} \\  \hline
TensorFlow  &  68.87\% \\
Theano  & 49.90\% \\
DyNet   & ... \\
\end{tabularx}

@@

\begin{tabularx}{\textwidth}{c|lll}
Metric 										& Dynet & TensorFlow & Theano \\ \hline
\texttt{\detokenize{achieved_occupancy}}			&		.	&		0.062			&		0.062		\\
\texttt{\detokenize{sm_efficiency}}					&		.	&		22.58\%			&		16.04\%		\\
\texttt{\detokenize{warp_efficiency}}					&		.	&		100.0\%			&		99.99\%		\\
\texttt{\detokenize{warp_nonpred_efficiency}}	&		.	&		99.95\%			&		99.91\%		\\
\texttt{\detokenize{global_hit_rate}}					&		.	&		0.00\%			&		0.00\%		\\
\texttt{\detokenize{local_hit_rate}}					&		.	&		0.00\%			&		0.00\%		\\
\texttt{\detokenize{dram_read_throughput}}*		&		.	&		11.07			&		9.97		\\
\texttt{\detokenize{dram_write_throughput}}**		&		.	&		411.99			&		503.54		\\
\end{tabularx}

\vspace{0.5em}
* GB/s \quad ** MB/s
}
